preprocess_human_recognition

### 2021-06-17 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
to download and preprocess recognition chunks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# compile all output csvs
```{r}
all_data=as_tibble()
for (batch in range(1,2)){
  this_batch = read.csv(paste0("csv_out/Devphotodraw_recognition_batch",batch,".csv")) %>% as_tibble() 
  all_data <- rbind(all_data, this_batch)
}

@@

used_all_options <- d %>%
  group_by(subID) %>%
  summarize(num_labels = length(unique(guessed_category)))

d <- d %>%
  filter(subID %in% included_subs$subID)
```

# quick check by age
```{r}
check_by_age <- d %>%
  group_by(age) %>%
  summarize(mean(guessed_category == drawn_category))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(here)
```

# compile all output csvs
```{r}
for (batch in 1:4){
  this_batch = read.csv(paste0("csv_out/",'batch',  batch, '_production_june2021.csv')) 
  if (batch==1) {
    all_data = this_batch
  }
  else {
    all_data <- all_data %>%
      full_join(this_batch)
  }
}

@@

# used_all_options <- d %>%
#   group_by(subID) %>%
#   summarize(num_labels = length(unique(guessed_category))) %>%
#   filter(num_labels==12)

d <- d %>%
  filter(subID %in% included_subs$subID) 
  # filter(subID %in% used_all_options$subID)
```

# Preprocess recognition data for merging with classificatinos, etc
```{r}
humans <- d %>%
  rename(category = drawn_category) %>%
  # get site and unique ids from filenanme
  mutate(unique_ids = str_split_fixed(imageName, '_',6)[,6]) %>%
  mutate(unique_ids = str_split_fixed(unique_ids, '.png',2)[,1]) %>%
  mutate(site = case_when( is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(unique_ids = case_when(site == "CDM" ~ str_split_fixed(unique_ids, '_',2)[,2],
                                site == "THU" ~ unique_ids)) %>%
  mutate(guessed_category = as.character(guessed_category)) %>%
  # clean up two guesses that somehow overrode drop down menU?
  mutate(guessed_category = case_when(guessed_category == "carn" ~ "car",
                                guessed_category == "hatb" ~ "hat",
                                TRUE ~ guessed_category)) %>%
  # make factors
  mutate(guessed_category = as.factor(guessed_category)) %>%
  mutate(unique_ids = as.factor(unique_ids)) %>%
  # calculate whether a guess was correct or not
  mutate(correct_or_not = guessed_category == category) %>%
  select(-subID)

```{r}
write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))
```
